Cryptanalysis of SBC based post-quantum signature scheme

### 2025-06-27 rapport.tex
ajout ptite photo

% !TeX spellcheck = en_US
% !TXS template
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper]{geometry}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[backend=bibtex,style=alphabetic]{biblatex}
\usepackage{csquotes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{stmaryrd}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{caption}

@@

@@

\author{Paul Mekhail\\ \textbf{Advisor:} Sorina Ionica}

@@

>>>>

% !TeX spellcheck = en_US
% !TXS template
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper]{geometry}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[backend=bibtex,style=alphabetic]{biblatex}
\usepackage{csquotes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{stmaryrd}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[affil-it]{authblk}

@@

\graphicspath{./}

@@

\author{Paul Mekhail
	\thanks{\texttt{paul.mekhail4@pm.me}}}
\affil{Laboratoire MIS, Université de Picardie Jules Verne, Amiens, France\\Sorbonne Université, Paris, France}

\author{\textbf{Advisor}: Sorina Ionica
	\thanks{\texttt{sorina.ionica@u-picardie.fr}}}
\affil{Laboratoire MIS, Université de Picardie Jules Verne, Amiens, France}

@@

		\begin{figure}[H]
			\begin{center}
				\includegraphics[scale=0.04]{unilasalle.jpg}
				\caption{UniLaSalle Engineering School, where the MIS offices are located(for now). Observant readers may notice the unusual UFO-like structure situated in front of the building.}
			\end{center}	
		\end{figure}
